---
title: "Bootstrap-Based Hypothesis Testing"
author: "Liam Bullen"
date: "30/11/2021"
output: html_document
---

Defining Data Simulation Functions
```{r}
library(fda)
#Defining data simulator for Function 1
curve <- function(par, m){
  t <- seq(0, 1, len = m)
  dat <- rep(0, m)
  for (i in 1:m){
  dat[i] <- 2-par*t[i]+par*exp(-100*(t[i]-0.5)^2)+rnorm(1, sd = 0.25)
  }
  dat
  }
#Defining simulator with random effects for Function 1
curve_cov <- function(par, m){
  t <- seq(0, 1, len = m)
  dat <- rep(0, m)
  for (i in 1:m){
  dat[i] <- 2-par*t[i]+par*exp(-100*(t[i]-0.5)^2)+rnorm(1, sd = 1)+ rnorm(1, sd = 0.25)
  }
  dat
}  
#Defining simulator for Function 2
curve_2 <- function(par, m){
  t <- seq(0.01, 1, len = m)
  dat <- rep(0, m)
  for (i in 1:m){
  dat[i] <- par*0.4*((par*t[i])^(-0.6))*exp(-(par*t[i])^0.4) + rnorm(1, sd = 0.25)
  }
  dat
} 
#Defining simulator with random effects for Function 2
curve_cov_2 <- function(par, m, a){
  t <- seq(0.01, 1, len = m)
  dat <- rep(0, m)
  for (i in 1:m){
  dat[i] <- par*0.4*((par*t[i])^(-0.6))*exp(-(par*t[i])^0.4)+rnorm(1, sd = a) + rnorm(1, sd = 0.25)
  }
  dat
} 
#Defining Cubic Spline smoothing function
Smoothing <- function(x, lam){
  knots <- t <- seq(0, 1, len = length(x))
  basis <- create.bspline.basis(c(min(t), max(t)), nbasis = length(t)+2)
  Lfd <- int2Lfd(2)
  lambda <- lam
  Par <- fdPar(basis, Lfd, lambda)
  smooth <- smooth.basis(argvals = t, y = x, fdParobj = Par)
  smooth
  }
```


Sample Curves of Function 1
```{r}
#Generate random base curve, par = 5 Function 1
t <- seq(0.01, 1, len = 100)
x <- curve(5, 100)
x.smooth <- Smoothing(x, 1e-5)
plot(x.smooth, xlab = "x", col = "gray")
curves.x <- data.frame(matrix(nrow = 100, ncol = 100))
for (i in 1:100){
x <- curve(5, 100)
x.smooth <- Smoothing(x, 1e-5)
lines(x.smooth, col ="gray")
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}
#Find mean curve
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
lines(cbind(t, mean.curve.x), lwd = 2)
legend("bottomleft",  c("Curve Samples", "Mean Curve"), col = c("gray", "black"), cex = 0.7, lty = 1)
```

Sample Curve of Function 2
```{r}
#Generate random base curve, par = 5 Function 1
t <- seq(0.01, 1, len = 100)
x <- curve_2(5, 100)
x.smooth <- Smoothing(x, 1e-5)
plot(x.smooth, xlab = "x", col = "gray")
curves.x <- data.frame(matrix(nrow = 100, ncol = 100))
for (i in 1:100){
x <- curve_2(5, 100)
x.smooth <- Smoothing(x, 1e-5)
lines(x.smooth, col ="gray")
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}
#Find mean curve
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
lines(cbind(t, mean.curve.x), lwd = 2)
legend("bottomleft",  c("Curve Samples", "Mean Curve"), col = c("gray", "black"), cex = 0.7, lty = 1)
```

Defining Bootstrap Functions
```{r}
Bootstrap_L1 <- function(curves.x, curves.y, B, R, n1, n2){
n <- n1+n2
#Mean Curve and Transformation
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
t.mean.x <- (mean.curve.x*mean.curve.x)/sum((mean.curve.x*mean.curve.x)*0.01)

mean.curve.y <- apply(curves.y, MARGIN = 1, mean)
t.mean.y <- (mean.curve.y*mean.curve.y)/sum((mean.curve.y*mean.curve.y)*0.01)

curves <- append(curves.x, curves.y)

#Build Statistic
L1 <- sum(abs(t.mean.x-t.mean.y))*0.01
L1.star <- rep(0, B)

for (i in 1:B){
#Create bootstrap samples and mean curves
index <- sample(1:n, n, rep = T)
x.star <- curves[index[1:n1]]
y.star <- curves[index[n1:n]]
x.star.mean <- apply(data.frame(x.star), MARGIN = 1, mean)
y.star.mean <- apply(data.frame(y.star), MARGIN = 1, mean)
t.x.star <- (x.star.mean*x.star.mean)/sum((x.star.mean*x.star.mean)*0.01)
t.y.star <- (y.star.mean*y.star.mean)/sum((y.star.mean*y.star.mean)*0.01)

#Compute test statistic star
L1.star[i] <- sum(abs(t.x.star-t.y.star))*0.01
}
#Find p-value
p.L1 <- (sum(L1.star > L1)+1)/(B+1)
p.L1
}

Bootstrap_ISD <- function(curves.x, curves.y, B, R, n1, n2){
n <- n1+n2
#Mean Curve and Transformation
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
t.mean.x <- (mean.curve.x*mean.curve.x)/sum((mean.curve.x*mean.curve.x)*0.01)

mean.curve.y <- apply(curves.y, MARGIN = 1, mean)
t.mean.y <- (mean.curve.y*mean.curve.y)/sum((mean.curve.y*mean.curve.y)*0.01)

curves <- append(curves.x, curves.y)

#Build Statistic
ISD <- sum((t.mean.x-t.mean.y)^2)*0.01
ISD.star <- rep(0, B)

for (i in 1:B){
#Create bootstrap samples and mean curves
index <- sample(1:n, n, rep = T)
x.star <- curves[index[1:n1]]
y.star <- curves[index[n1:n]]
x.star.mean <- apply(data.frame(x.star), MARGIN = 1, mean)
y.star.mean <- apply(data.frame(y.star), MARGIN = 1, mean)
t.x.star <- (x.star.mean*x.star.mean)/sum((x.star.mean*x.star.mean)*0.01)
t.y.star <- (y.star.mean*y.star.mean)/sum((y.star.mean*y.star.mean)*0.01)

#Compute test statistic star
ISD.star[i] <- sum((t.x.star-t.y.star)^2)*0.01
}
#Find p-value
p.ISD <- (sum(ISD.star > ISD)+1)/(B+1)
p.ISD
}

Bootstrap_KL <- function(curves.x, curves.y, B, R, n1, n2){
n <- n1+n2
#Mean Curve and Transformation
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
t.mean.x <- (mean.curve.x*mean.curve.x)/sum((mean.curve.x*mean.curve.x)*0.01)

mean.curve.y <- apply(curves.y, MARGIN = 1, mean)
t.mean.y <- (mean.curve.y*mean.curve.y)/sum((mean.curve.y*mean.curve.y)*0.01)

curves <- append(curves.x, curves.y)

#Build Statistic
KL <- sum((log(t.mean.x)-log(t.mean.y))*t.mean.x)*0.01
KL.star <- rep(0, B)

for (i in 1:B){
#Create bootstrap samples and mean curves
index <- sample(1:n, n, rep = T)
x.star <- curves[index[1:n1]]
y.star <- curves[index[n1:n]]
x.star.mean <- apply(data.frame(x.star), MARGIN = 1, mean)
y.star.mean <- apply(data.frame(y.star), MARGIN = 1, mean)
t.x.star <- (x.star.mean*x.star.mean)/sum((x.star.mean*x.star.mean)*0.01)
t.y.star <- (y.star.mean*y.star.mean)/sum((y.star.mean*y.star.mean)*0.01)

#Compute test statistic star
KL.star[i] <- sum((log(t.x.star)-log(t.y.star))*t.x.star)*0.01
}
#Find p-value
p.KL <- (sum(KL.star > KL)+1)/(B+1)
p.KL
}

Bootstrap_Hellinger <- function(curves.x, curves.y, B, R, n1, n2){
n <- n1+n2
#Mean Curve and Transformation
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
t.mean.x <- (mean.curve.x*mean.curve.x)/sum((mean.curve.x*mean.curve.x)*0.01)

mean.curve.y <- apply(curves.y, MARGIN = 1, mean)
t.mean.y <- (mean.curve.y*mean.curve.y)/sum((mean.curve.y*mean.curve.y)*0.01)

curves <- append(curves.x, curves.y)

#Build Statistic
Hel <- sqrt(sum((sqrt(t.mean.x)-sqrt(t.mean.y))^2)*0.01)
Hel.star <- rep(0, B)

for (i in 1:B){
#Create bootstrap samples and mean curves
index <- sample(1:n, n, rep = T)
x.star <- curves[index[1:n1]]
y.star <- curves[index[n1:n]]
x.star.mean <- apply(data.frame(x.star), MARGIN = 1, mean)
y.star.mean <- apply(data.frame(y.star), MARGIN = 1, mean)
t.x.star <- (x.star.mean*x.star.mean)/sum((x.star.mean*x.star.mean)*0.01)
t.y.star <- (y.star.mean*y.star.mean)/sum((y.star.mean*y.star.mean)*0.01)

#Compute test statistic star
Hel.star[i] <- sqrt(sum((sqrt(t.x.star)-sqrt(t.y.star))^2)*0.01)
}
#Find p-value
p.Hel <- (sum(Hel.star > Hel)+1)/(B+1)
p.Hel
}

Bootstrap_Affinity <- function(curves.x, curves.y, B, R, n1, n2){
n <- n1+n2
#Mean Curve and Transformation
mean.curve.x <- apply(curves.x, MARGIN = 1, mean)
t.mean.x <- (mean.curve.x*mean.curve.x)/sum((mean.curve.x*mean.curve.x)*0.01)

mean.curve.y <- apply(curves.y, MARGIN = 1, mean)
t.mean.y <- (mean.curve.y*mean.curve.y)/sum((mean.curve.y*mean.curve.y)*0.01)

curves <- append(curves.x, curves.y)

#Build Statistic
Aff <- sum(sqrt(t.mean.x*t.mean.y))*0.01
Aff.star <- rep(0, B)

for (i in 1:B){
#Create bootstrap samples and mean curves
index <- sample(1:n, n, rep = T)
x.star <- curves[index[1:n1]]
y.star <- curves[index[n1:n]]
x.star.mean <- apply(data.frame(x.star), MARGIN = 1, mean)
y.star.mean <- apply(data.frame(y.star), MARGIN = 1, mean)
t.x.star <- (x.star.mean*x.star.mean)/sum((x.star.mean*x.star.mean)*0.01)
t.y.star <- (y.star.mean*y.star.mean)/sum((y.star.mean*y.star.mean)*0.01)

#Compute test statistic star
Aff.star[i] <- sum(sqrt(t.x.star*t.y.star))*0.01
}
#Find p-value
p.Aff <- (sum(Aff.star < Aff)+1)/(B+1)
p.Aff
}
```

Final Bootstrap Function
```{r}
Bootstrap_FDA <- function(method, curves.x, curves.y, B, R, n1, n2){
  if(method == "L"){
    Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
  }
  else if(method == "I"){
    Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
  }
  else if(method == "K"){
    Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
  }
  else if(method == "H"){
    Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
  }
  else if(method == "A"){
    Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
  }
}

```

Scenario 1
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 50
n2 <- 50
lam1 <- 1e-5
lam2 <- 1e-5
par2 <- c(4.92, 4.94, 4.96, 4.98, 5.00, 5.02, 5.04, 5.06, 5.08)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve(5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}
```

Scenario 1 Results
```{r}
params <- c(4.92, 4.94, 4.96, 4.98, 5, 5.02, 5.04, 5.06, 5.08)
L1_1 <- cbind(params, L1.Rej)
ISD_1 <- cbind(params, ISD.Rej)
KL_1 <- cbind(params, KL.Rej)
Hel_1 <- cbind(params, Hellinger.Rej)
Aff_1 <- cbind(params, Affinity.Rej)
```

Scenario 1 Plotting
```{r}
#Power Function Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_1_1.pdf")
plot(L1_1, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 1")
lines(ISD_1, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Power Function Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_1_2.pdf")
plot(KL_1, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_1, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```

Scenario 2
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 50
n2 <- 100
lam1 <- 1e-5
lam2 <- 1e-5
par2 <- c(4.92, 4.94, 4.96, 4.98, 5.00, 5.02, 5.04, 5.06, 5.08)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve(5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}

```

Scenario 2 Results
```{r}
params <- c(4.92, 4.94, 4.96, 4.98, 5, 5.02, 5.04, 5.06, 5.08)
L1_2 <- cbind(params, L1.Rej)
ISD_2 <- cbind(params, ISD.Rej)
KL_2 <- cbind(params, KL.Rej)
Hel_2 <- cbind(params, Hellinger.Rej)
Aff_2 <- cbind(params, Affinity.Rej)
```

Scenario 2 Plotting
```{r}
#Power Function Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_2_1.pdf")
plot(L1_2, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 2")
lines(ISD_2, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Power Function Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_2_2.pdf")
plot(KL_2, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_2, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```

Scenario 3 (Function 1)
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 200
n2 <- 200
lam1 <- 1e-5
lam2 <- 1e-5
par2 <- c(4.92, 4.94, 4.96, 4.98, 5.00, 5.02, 5.04, 5.06, 5.08)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve(5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}

```

Scenario 3 Results (Function 1)
```{r}
params <- c(4.92, 4.94, 4.96, 4.98, 5, 5.02, 5.04, 5.06, 5.08)
L1_3 <- cbind(params, L1.Rej)
ISD_3 <- cbind(params, ISD.Rej)
KL_3 <- cbind(params, KL.Rej)
Hel_3 <- cbind(params, Hellinger.Rej)
Aff_3 <- cbind(params, Affinity.Rej)
```

Scenario 3 Plotting (Function 1)
```{r}
#Power Function Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_3_1.pdf")
plot(L1_3, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 3")
lines(ISD_3, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Power Function Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_3_2.pdf")
plot(KL_3, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_3, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```

Scenario 4(Function 1)
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 200
n2 <- 200
lam1 <- 1e-5
lam2 <- 1e-5
par2 <- c(4.92, 4.94, 4.96, 4.98, 5.00, 5.02, 5.04, 5.06, 5.08)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve_cov(5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve_cov(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}
```

Scenario 4 Results (Function 1)
```{r}
params <- c(4.92, 4.94, 4.96, 4.98, 5, 5.02, 5.04, 5.06, 5.08)
L1_4 <- cbind(params, L1.Rej)
ISD_4 <- cbind(params, ISD.Rej)
KL_4 <- cbind(params, KL.Rej)
Hel_4 <- cbind(params, Hellinger.Rej)
Aff_4 <- cbind(params, Affinity.Rej)
```

Scenario 4 Plotting (Function 1)
```{r}
#Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_4_1.pdf")
plot(L1_4, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 4")
lines(ISD_4, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_4_2.pdf")
plot(KL_4, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_4, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```

Scenario 3 (Function 2)
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 200
n2 <- 200
lam1 <- 1e-4
lam2 <- 1e-4
par2 <- c(1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve_2(1.5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve_2(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}
```


Scenario 3 Results (Function 2)
```{r}
params <- c(1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9)
L1_5 <- cbind(params, L1.Rej)
ISD_5 <- cbind(params, ISD.Rej)
KL_5 <- cbind(params, KL.Rej)
Hel_5 <- cbind(params, Hellinger.Rej)
Aff_5 <- cbind(params, Affinity.Rej)
```

Scenario 3 Plotting (Function 2)
```{r}
#Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_5_1.pdf")
plot(L1_5, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 3")
lines(ISD_5, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_5_2.pdf")
plot(KL_5, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_5, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```

Scenario 4 (Function 2)
```{r}
#Defining Variables
B <- 75
R <- 100
n1 <- 200
n2 <- 200
lam1 <- 1e-4
lam2 <- 1e-4
par2 <- c(1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9)

#Finding Empirical Rejection Probability
L1.Rej <- rep(1, length(par2))
for (p in 1:length(par2)){
P.L1 <- rep(1, R)
for (j in 1:R){
#Generate Curves
curves.x <- data.frame(matrix(nrow = 100, ncol = n1))
for (i in 1:n1){
x <- curve_cov_2(1.5, 100)
x.smooth <- Smoothing(x, lam1)
curves.x[,i] <- eval.fd(t, x.smooth$fd)
}

curves.y <- data.frame(matrix(nrow = 100, ncol = n2))
for (i in 1:n2){
y <- curve_cov_2(par2[p], 100)
y.smooth <- Smoothing(y, lam2)
curves.y[,i] <- eval.fd(t, y.smooth$fd)
}
#Run Bootstrap Test
p.L1[j] <- Bootstrap_L1(curves.x, curves.y, B, R, n1, n2)
p.ISD[j] <- Bootstrap_ISD(curves.x, curves.y, B, R, n1, n2)
p.Hel[j]<-Bootstrap_Hellinger(curves.x, curves.y, B, R, n1, n2)
p.KL[j] <- Bootstrap_KL(curves.x, curves.y, B, R, n1, n2)
p.Aff[j] <- Bootstrap_Affinity(curves.x, curves.y, B, R, n1, n2)
}
#Empirical Rejection
L1.prob <- sum(p.L1<0.05)/R
ISD.prob <- sum(p.ISD<0.05)/R
Hellinger.prob <- sum(p.Hel<0.05)/R
KL.prob <- sum(p.KL<0.05)/R
Affinity.prob <- sum(p.Aff<0.05)/R

L1.Rej[p] <- L1.prob
ISD.Rej[p] <- ISD.prob
Hellinger.Rej[p] <- Hellinger.prob
KL.Rej[p] <- KL.prob
Affinity.rej[p] <- Affinity.prob
}
```

Scenario 4 Results (Function 2)
```{r}
params <- c(1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9)
L1_6 <- cbind(params, L1.Rej)
ISD_6 <- cbind(params, ISD.Rej)
KL_6 <- cbind(params, KL.Rej)
Hel_6 <- cbind(params, Hellinger.Rej)
Aff_6 <- cbind(params, Affinity.Rej)
```

Scenario 4 Plotting (Function 2)
```{r}
#Plot 1
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_6_1.pdf")
plot(L1_6, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b", main = "Scenario 4")
lines(ISD_6, type = "b", pch = 15)
legend("top",  c("L1", "ISD"), cex = 0.7, pch = c(21,15))
dev.off()

#Plot 2
pdf("/Users/liamb/School/Western/4th Year - 1st Semester/4999 (Statistics)/scen_6_2.pdf")
plot(KL_6, xlab = "Parameter", ylab = "Power Function", pch = 21, type = "b")
lines(Hel_6, type = "b", pch = 15)
legend("top",  c("Kullback-Leibler", "Hellinger"), cex = 0.7, pch = c(21,15))
dev.off()
```


Growth Data Application
```{r}
#Defining Variables
n1 <- 54
n2 <- 39
t <- 
n <- n1 + n2
B <- 100

#Splitting Growth Data into Datasets for boy and girl
curves.x <- data.frame(matrix(nrow = 31, ncol = n1))
for (i in 1:n1){
curves.x[,i] <- growth$hgtf[,i]
}

curves.y <- data.frame(matrix(nrow = 31, ncol = n2))
for (i in 1:n2){
curves.y[,i] <- growth$hgtm[, i]
}

#Running Test of 2 best statistics
P_ISD <- Bootstrap_ISD(curves.x, curves.y, B, R, t, n1, n2)
P_KL <- Bootstrap_KL(curves.x, curves.y, B, R, t, n1, n2)
P_ISD
P_KL
```
